\documentclass{article}
\usepackage{amsmath}

\begin{document}

\section*{Diamond Model Classification of Questions}

The Diamond Model of Intrusion Analysis is a structured framework that connects four core features of any malicious cyber activity: Adversary, Capability, Infrastructure, and Victim. The questions listed below can be categorized within the Diamond Model based on these core features:

\begin{itemize}
    \item \textbf{What is MAJORCA?}
    \begin{itemize}
        \item \textbf{Explanation:} This question pertains to a specific \textit{Capability} used by an \textit{Adversary} in cyber operations.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature of the Diamond Model as it inquires about a tool used by an adversary.
    \end{itemize}
    
    \item \textbf{How does MAJORCA automatically generate ROP and JOP payloads for x86 and MIPS?}
    \begin{itemize}
        \item \textbf{Explanation:} This question delves into the technical \textit{Capability} of MAJORCA to generate payloads.
        \item \textbf{Diamond Model Feature:} This question relates to the \textit{Capability} feature, exploring the technical functions of the MAJORCA tool.
    \end{itemize}
    
    \item \textbf{What does MAJORCA outperform?}
    \begin{itemize}
        \item \textbf{Explanation:} This question compares the \textit{Capability} of MAJORCA with other tools or methods.
        \item \textbf{Diamond Model Feature:} This question is concerned with the \textit{Capability} feature, focusing on MAJORCA's performance.
    \end{itemize}
    
    \item \textbf{What is AFLSmart?}
    \begin{itemize}
        \item \textbf{Explanation:} This question is about another \textit{Capability} used for fuzz testing.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, addressing the functionality of AFLSmart.
    \end{itemize}
    
    \item \textbf{What is Stand-in Backdoor?}
    \begin{itemize}
        \item \textbf{Explanation:} This question refers to a specific \textit{Capability} used to gain unauthorized access.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, describing the Stand-in Backdoor.
    \end{itemize}

    \item \textbf{How can the attacker inject mappings of triggers and misclassification rules into the victim model?}
    \begin{itemize}
        \item \textbf{Explanation:} This question addresses the method (\textit{Capability}) an \textit{Adversary} uses to manipulate a \textit{Victim}'s model.
        \item \textbf{Diamond Model Feature:} This question pertains to both \textit{Adversary} and \textit{Capability} features, focusing on the attack method.
    \end{itemize}

    \item \textbf{What is the key to performing DNS brute forcing?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the \textit{Infrastructure} required for DNS brute forcing.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Infrastructure} feature, discussing the technical aspects of DNS brute forcing.
    \end{itemize}

    \item \textbf{FluBot and Exodus Spyware are the most recent and notorious examples of what?}
    \begin{itemize}
        \item \textbf{Explanation:} This question pertains to specific \textit{Adversaries} and their \textit{Capabilities}.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Adversary} and \textit{Capability} features, identifying recent malicious tools.
    \end{itemize}

    \item \textbf{Fuze and KOOBE are two studies that target what two types of memory?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves specific \textit{Capabilities} targeting different types of memory.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, focusing on memory exploitation techniques.
    \end{itemize}

    \item \textbf{What reflects the persistent efforts of cybercriminals to bypass security measures and exploit new vulnerabilities?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the ongoing \textit{Adversary} activities and their evolving \textit{Capabilities}.
        \item \textbf{Diamond Model Feature:} This question relates to both \textit{Adversary} and \textit{Capability} features, highlighting the dynamic nature of cyber threats.
    \end{itemize}

    \item \textbf{When did Beast emerge?}
    \begin{itemize}
        \item \textbf{Explanation:} This question focuses on the timeline (\textit{Meta-feature}) of a specific \textit{Capability}.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} and \textit{Meta-feature} (time) of Beast.
    \end{itemize}

    \item \textbf{When was Beast released?}
    \begin{itemize}
        \item \textbf{Explanation:} Similar to the previous question, it concerns the release date (\textit{Meta-feature}) of a \textit{Capability}.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} and \textit{Meta-feature} (time) of Beast.
    \end{itemize}

    \item \textbf{Ransomware originated with the AIDS Trojan and evolved with what programs?}
    \begin{itemize}
        \item \textbf{Explanation:} This question examines the evolution of a specific \textit{Capability} over time.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, discussing the historical development of ransomware.
    \end{itemize}

    \item \textbf{How can we run and test the binary of MCU firmware via dynamic symbolic execution at scale and support the interrupt on demand?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the technical \textit{Capability} of testing firmware.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, focusing on dynamic symbolic execution.
    \end{itemize}

    \item \textbf{What is the purpose of mutating the inputs that may alter the program execution path to generate well-formed test inputs?}
    \begin{itemize}
        \item \textbf{Explanation:} This question pertains to the \textit{Capability} of generating test inputs.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, discussing input mutation.
    \end{itemize}

    \item \textbf{How does fixing vulnerabilities depend heavily on manually generating repair templates?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the \textit{Capability} of fixing vulnerabilities.
        \item \textbf{Diamond Model Feature:} This question relates to the \textit{Capability} feature, focusing on repair templates.
    \end{itemize}

    \item \textbf{What is APR?}
    \begin{itemize}
        \item \textbf{Explanation:} This question defines a specific \textit{Capability} in the context of vulnerability repair.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, explaining APR.
    \end{itemize}

    \item \textbf{What are some APR studies focused on?}
    \begin{itemize}
        \item \textbf{Explanation:} This question explores the focus areas of studies on a \textit{Capability}.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, discussing APR research.
    \end{itemize}

    \item \textbf{What is DR. CHECKER?}
    \begin{itemize}
        \item \textbf{Explanation:} This question identifies a specific \textit{Capability} for static analysis.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, explaining DR. CHECKER.
    \end{itemize}

    \item \textbf{How many RCRO chains does the countermeasure need to be effective on the ZCU104 board?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the technical details (\textit{Capability}) of a countermeasure.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, discussing RCRO chains.
    \end{itemize}

    \item \textbf{How many unknown hardware bugs were found in SurgeFuzz?}
    \begin{itemize}
        \item \textbf{Explanation:} This question focuses on the results (\textit{Capability}) of a fuzzing tool.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, discussing hardware bug detection.
    \end{itemize}

    \item \textbf{What is the scheduling algorithm to angr in order to improve the efficiency of performing?}
    \begin{itemize}
        \item \textbf{Explanation:} This question addresses the technical \textit{Capability} of a scheduling algorithm.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, focusing on angr's scheduling algorithm.
    \end{itemize}

    \item \textbf{How can Buttercup be used to detect off-by-one overflows?}
    \begin{itemize}
        \item \textbf{Explanation:} This question pertains to a specific \textit{Capability} for detecting buffer overflows.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, discussing Buttercup.
    \end{itemize}

    \item \textbf{What is the problem of determining the return address to exploit a buffer overflow vulnerability?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the technical challenge (\textit{Capability}) of exploiting a buffer overflow.
        \item \textbf{Diamond Model Feature:} This question relates to the \textit{Capability} feature, focusing on return address determination.
    \end{itemize}

    \item \textbf{What is a dynamic symbolic execution mechanism specifically designed for USB controller firmware?}
    \begin{itemize}
        \item \textbf{Explanation:} This question describes a specific \textit{Capability} for USB firmware analysis.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, discussing a symbolic execution mechanism.
    \end{itemize}

    \item \textbf{What is the name of the novel approach to exploit historical vulnerability fixes?}
    \begin{itemize}
        \item \textbf{Explanation:} This question identifies a specific \textit{Capability} for exploiting past vulnerability fixes.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, naming a novel approach.
    \end{itemize}

    \item \textbf{What does SeqTrans: Automatic Vulnerability Fix Via Sequence to Sequence Learning do?}
    \begin{itemize}
        \item \textbf{Explanation:} This question explains the functionality (\textit{Capability}) of SeqTrans.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, describing SeqTrans.
    \end{itemize}

    \item \textbf{SeqTrans outperforms the latest techniques and achieves what percentage in statement-level fix?}
    \begin{itemize}
        \item \textbf{Explanation:} This question compares the performance (\textit{Capability}) of SeqTrans.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, focusing on SeqTrans's performance.
    \end{itemize}

    \item \textbf{What has been developed to provide valuable insights into the types and locations of bugs that exist in critical kernel code?}
    \begin{itemize}
        \item \textbf{Explanation:} This question pertains to a specific \textit{Capability} for kernel code analysis.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, discussing insights into kernel bugs.
    \end{itemize}

    \item \textbf{What is the name of the bug detector used by DR. CHECKER?}
    \begin{itemize}
        \item \textbf{Explanation:} This question identifies a specific \textit{Capability} used by DR. CHECKER.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, naming the bug detector.
    \end{itemize}

    \item \textbf{What mechanism enables dynamic symbolic execution to effectively cover diverse interrupt-dependent code in the firmware?}
    \begin{itemize}
        \item \textbf{Explanation:} This question describes a specific \textit{Capability} for firmware analysis.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, focusing on interrupt-dependent code coverage.
    \end{itemize}

    \item \textbf{How does Buttercup detect real-time traffic containing an attack?}
    \begin{itemize}
        \item \textbf{Explanation:} This question explores the \textit{Capability} of Buttercup to detect attacks.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, discussing real-time attack detection.
    \end{itemize}

    \item \textbf{How does BOWAll protect against buffer over-flows?}
    \begin{itemize}
        \item \textbf{Explanation:} This question pertains to a specific \textit{Capability} for protecting against buffer overflows.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, focusing on BOWAll.
    \end{itemize}

    \item \textbf{What is ADMutate?}
    \begin{itemize}
        \item \textbf{Explanation:} This question identifies a specific \textit{Capability} for dynamic binary modification.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, explaining ADMutate.
    \end{itemize}

    \item \textbf{What exploited network vulnerabilities and used social engineering to spread and infect millions of computers?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves an \textit{Adversary} using \textit{Capabilities} to exploit network vulnerabilities.
        \item \textbf{Diamond Model Feature:} This question pertains to both \textit{Adversary} and \textit{Capability} features, discussing a widespread attack method.
    \end{itemize}

    \item \textbf{Where were almost all design bugs in the OpenSPARC processor found?}
    \begin{itemize}
        \item \textbf{Explanation:} This question addresses the \textit{Infrastructure} of the OpenSPARC processor.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Infrastructure} feature, focusing on design bug locations.
    \end{itemize}

    \item \textbf{What is the major difference between fuzzing in RTL designs and CPU designs?}
    \begin{itemize}
        \item \textbf{Explanation:} This question compares \textit{Capabilities} in different design contexts.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, discussing fuzzing differences.
    \end{itemize}

    \item \textbf{DirectFuzz intensively verifies a target module by preferentially mutating inputs that increase the coverage of modules close to what?}
    \begin{itemize}
        \item \textbf{Explanation:} This question explores a specific \textit{Capability} of DirectFuzz for module verification.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, discussing input mutation strategies.
    \end{itemize}

    \item \textbf{DirectFuzz can explore a specific part of the state space but is not able to explore the corner case in what?}
    \begin{itemize}
        \item \textbf{Explanation:} This question discusses the limitations (\textit{Capability}) of DirectFuzz.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, focusing on state space exploration.
    \end{itemize}

    \item \textbf{What demonstrates that SurgeFuzz can generate surge-inducing programs more effectively than the existing methods?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the performance (\textit{Capability}) of SurgeFuzz.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, comparing SurgeFuzz's effectiveness.
    \end{itemize}

    \item \textbf{What shows that SurgeFuzz can detect various bugs faster and with higher probability than the existing methods?}
    \begin{itemize}
        \item \textbf{Explanation:} This question examines the detection \textit{Capability} of SurgeFuzz.
        \item \textbf{Diamond Model Feature:} This question relates to the \textit{Capability} feature, discussing bug detection efficiency.
    \end{itemize}

    \item \textbf{What was the first researcher to determine that Stuxnet was a cyberwarfare attack against Iran?}
    \begin{itemize}
        \item \textbf{Explanation:} This question identifies an \textit{Adversary} and their \textit{Capability}.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Adversary} and \textit{Capability} features, discussing Stuxnet.
    \end{itemize}

    \item \textbf{What happens when Stuxnets dropper loads rogue code to the controller?}
    \begin{itemize}
        \item \textbf{Explanation:} This question explores the \textit{Capability} and its impact on the \textit{Victim}'s infrastructure.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} and \textit{Victim} features, discussing the payload effects.
    \end{itemize}

    \item \textbf{What is the infamous DEADFOOT condition?}
    \begin{itemize}
        \item \textbf{Explanation:} This question addresses a specific \textit{Capability} leading to a critical failure.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, explaining the DEADFOOT condition.
    \end{itemize}

    \item \textbf{How many commits did SeqTrans fix in 205 Java projects?}
    \begin{itemize}
        \item \textbf{Explanation:} This question focuses on the performance (\textit{Capability}) of SeqTrans.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, discussing the number of fixes.
    \end{itemize}

    \item \textbf{What does ADMutate dynamically modify?}
    \begin{itemize}
        \item \textbf{Explanation:} This question explores the dynamic modification (\textit{Capability}) by ADMutate.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Capability} feature, discussing dynamic modifications.
    \end{itemize}

    \item \textbf{What did Buttercup compare to Snort?}
    \begin{itemize}
        \item \textbf{Explanation:} This question involves the comparative performance (\textit{Capability}) of Buttercup and Snort.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Capability} feature, focusing on comparison with Snort.
    \end{itemize}

    \item \textbf{What was the purpose of Buttercup?}
    \begin{itemize}
        \item \textbf{Explanation:} This question explores the intended use (\textit{Capability}) of Buttercup.
        \item \textbf{Diamond Model Feature:} This question is related to the \textit{Capability} feature, discussing Buttercup's purpose.
    \end{itemize}

    \item \textbf{What is a more significant factor in QoS degradation than cryptographic cost?}
    \begin{itemize}
        \item \textbf{Explanation:} This question examines a specific \textit{Infrastructure} issue affecting QoS.
        \item \textbf{Diamond Model Feature:} This question pertains to the \textit{Infrastructure} feature, discussing QoS degradation.
    \end{itemize}

    \item \textbf{The 802.1x-EAP-TLS policy is best suitable for what?}
    \begin{itemize}
        \item \textbf{Explanation:} This question addresses the application (\textit{Infrastructure}) of a security policy.
        \item \textbf{Diamond Model Feature:} This question belongs to the \textit{Infrastructure} feature, focusing on the 802.1x-EAP-TLS policy.
    \end{itemize}
\end{itemize}

\end{document}
